Model LF

### 2022-11-23 max_dp endogen stød.Rmd
Commit

@@

@@

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
### Unemployment rate

>>>>

**Macro effect without productivity wages, and LF**

```{r}
change_unemp_pr_04= (unemp_04 - unemp_bs4)/unemp_bs4
change_dp_person_pr_04= (dp_person_04 - dp_person_bs4)/dp_person_bs4
```

```{r}
e3= change_unemp_pr_04/change_dp_person_pr_04;e3
```

**Macro effect without productivity**

@@

```{r}
change_unemp_pr_08= (unemp_08 - unemp_bs8)/unemp_bs8
change_dp_person_pr_08= (dp_person_08 - dp_person_bs8)/dp_person_bs8
```

```{r}
e3= change_unemp_pr_08/change_dp_person_pr_08;e3
```

@@

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
macro_elas_short= 0.25
macro_elas_nowage_short= -0.05
### Unemployment rate
